\normalfont\textbf{ \Large {Reducing data traffic in wireless structural health monitoring systems using embedded computing}}

### 2015-02-09 Paper/PaperJahrSchlichSHM.tex
Reworked all figures to include latex's sans-serif-font

\documentclass[12pt,a4paper]{scrartcl}
\usepackage[ngerman, english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[color=yellow!15]{todonotes}
\usepackage{graphicx}
\usepackage[numbers, sort&compress, square]{natbib}
\usepackage[colorlinks, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{titlesec}
\usepackage{color}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[scale=0.4]{figures/teststructure.jpg}
    \caption{Laboratory setup}
    \label{fig:teststructure}
\end{figure}

@@

The correct implementation of the FFT has been verified beforehand by plotting the frequency domain of various oscillation events.
\autoref{fig:fft-diagram} shows  one of the results as an example.
The natural frequencies are readily identifiable by the peaks in the diagram.
The first three natural frequencies are located at approximately 2.3\,Hz (first natural frequency), 8\,Hz (second natural frequency),and 16\,Hz (third natural frequency).
The same natural frequencies appeared throughout repeated tests with varying excitation forces, sampling rates, and number of measurements.

\begin{table}[ht]
	\centering
	\begin{tabular}{c c c}
		1\textsuperscript{st} natural frequency & 2\textsuperscript{nd} natural frequency & 3\textsuperscript{rd} natural frequency \\ 
		2,3 & 8 & 16 \\
	\end{tabular}
	\caption{Natural frequencies of the test structure}
	\label{tab:nat-freqs}
\end{table}

\begin{itemize}
	\item 
	\item that means our paper is also wireless and very very good
\end{itemize}

>>>>

\documentclass[12pt,a4paper]{scrartcl}
\usepackage[ngerman, english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[color=yellow!15]{todonotes}
\usepackage{graphicx}
\usepackage[numbers, sort&compress, square]{natbib}
\usepackage[colorlinks, linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\usepackage{titlesec}
\usepackage{color}
\usepackage{booktabs}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale=0.6]{figures/testsetup.png}
    \caption{Laboratory setup}
    \label{fig:teststructure}
\end{figure}

@@

The correct implementation of the FFT has been verified beforehand by plotting the frequency domain of various oscillation events.
\autoref{fig:50hzfft} shows  one of the results as an example.
The natural frequencies are readily identifiable by the peaks in the diagram.
The first three natural frequencies are located at approximately 2.3\,Hz (1\textsuperscript{st} natural frequency), 8\,Hz (2\textsuperscript{nd} natural frequency),and 18\,Hz (3\textsuperscript{rd} natural frequency).
The same natural frequencies appeared throughout repeated tests with varying excitation forces, sampling rates, and number of measured acceleration values.

\begin{figure}[ht]
    \centering
    \includegraphics{figures/50Hz.pdf}
    \caption{frequency domain graph of the oscillation}
    \label{fig:50hzfft}
\end{figure}

After the

%\begin{table}[ht]
%	\centering
%	\begin{tabular}{c c c}
%		\toprule
%		1\textsuperscript{st} natural frequency & 2\textsuperscript{nd} natural frequency & 3\textsuperscript{rd} natural frequency \\ 
%		\midrule
%		2,3 & 8 & 16 \\
%		\bottomrule
%	\end{tabular}
%	\caption{Natural frequencies of the test structure}
%	\label{tab:nat-freqs}
%\end{table}
